---
title: "ANT_analysis_OverallAlerting"
author: "Jeanette Popovova"
date: "1/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
### Libraries
library(tidyverse) # for data wrangling and plotting
source('rtfmri_theme.R')
source('rtfmri_theme2.R')
```

#Alerting Effect Analysis


## 1. Loading ANT data


```{r, echo = FALSE, include=FALSE}
path = 'C:/Users/Jeane/Documents/PhD/Behavior_Analysis/ANTwrongName/'

bids_folder =  'C:/Users/Jeane/Documents/PhD/Behavior_Analysis/'


### Messy naming conventions up to participant 12 

## Manual wrangling


## VP006

sub.vp006.ses.01.pant <- read_csv(file = paste(path,'jVP006_1/ANT-jVP006_1.csv', sep = '')) %>% 
  mutate(subid = 'VP006',
         session = '1')

sub.vp006.ses.03.pant <- read_csv(file = paste(path,'VP006_03/ANT-VP006_03.csv', sep = '')) %>% 
  mutate(subid = 'VP006',
         session = '3')

sub.vp006.ses.04.pant <- read_csv(file = paste(path,'VP006_04/ANT-VP006_04.csv', sep = '')) %>% 
  mutate(subid = 'VP006',
         session = '4')


sub.vp006 <- bind_rows(sub.vp006.ses.01.pant,sub.vp006.ses.03.pant, sub.vp006.ses.04.pant) 


## VP007

sub.vp007.ses.01.pant <- read_csv(file = paste(path,'VP007_01/ANT-VP007_01.csv', sep = '')) %>% 
  mutate(subid = 'VP007',
         session = '1')

sub.vp007.ses.03.pant <- read_csv(file = paste(path,'VP007_02/ANT-VP007_02.csv', sep = '')) %>% 
  mutate(subid = 'VP007',
         session = '3')

sub.vp007.ses.04.pant <- read_csv(file = paste(path,'VP007_04/ANT-VP007_04.csv', sep = '')) %>% 
  mutate(subid = 'VP007',
         session = '4')


sub.vp007 <- bind_rows(sub.vp007.ses.01.pant,sub.vp007.ses.03.pant, sub.vp007.ses.04.pant) 

## VP008

sub.vp008.ses.01.pant <- read_csv(file = paste(path,'VP008_01/ANT-VP008_01.csv', sep = '')) %>% 
  mutate(subid = 'VP008',
         session = '1')

sub.vp008.ses.03.pant <- read_csv(file = paste(path,'VP008_02/ANT-VP008_02.csv', sep = '')) %>% 
  mutate(subid = 'VP008',
         session = '3')

sub.vp008.ses.04.pant <- read_csv(file = paste(path,'VP008_04/ANT-VP008_04.csv', sep = '')) %>% 
  mutate(subid = 'VP008',
         session = '4')

sub.vp008 <- bind_rows(sub.vp008.ses.01.pant,sub.vp008.ses.03.pant, sub.vp008.ses.04.pant) 

## VP009

sub.vp009.ses.01.pant <- read_csv(file = paste(path,'VP009_01/ANT-VP009_01.csv', sep = '')) %>% 
  mutate(subid = 'VP009',
         session = '1')

sub.vp009.ses.03.pant <- read_csv(file = paste(path,'VP009_02/ANT-VP009_02.csv', sep = '')) %>% 
  mutate(subid = 'VP009',
         session = '3')

sub.vp009.ses.04.pant <- read_csv(file = paste(path,'VP009_04/ANT-VP009_04.csv', sep = '')) %>% 
  mutate(subid = 'VP009',
         session = '4')


sub.vp009 <- bind_rows(sub.vp009.ses.01.pant,sub.vp009.ses.03.pant, sub.vp009.ses.04.pant) 


## VP010

sub.vp010.ses.01.pant <- read_csv(file = paste(path,'VP010_01/ANT-VP010_01.csv', sep = '')) %>% 
  mutate(subid = 'VP010',
         session = '1')

sub.vp010.ses.03.pant <- read_csv(file = paste(path,'VP010_2/ANT-VP010_2.csv', sep = '')) %>% 
  mutate(subid = 'VP010',
         session = '3')

sub.vp010.ses.04.pant <- read_csv(file = paste(path,'VP010_04/ANT-VP010_04.csv', sep = '')) %>% 
  mutate(subid = 'VP010',
         session = '4')

sub.vp010 <- bind_rows(sub.vp010.ses.01.pant,sub.vp010.ses.03.pant, sub.vp010.ses.04.pant) 

## VP011

sub.vp011.ses.01.pant <- read_csv(file = paste(path,'VP011/ANT-VP011.csv', sep = '')) %>% 
  mutate(subid = 'VP011',
         session = '1')

sub.vp011.ses.03.pant <- read_csv(file = paste(path,'VP011_02/ANT-VP011_02.csv', sep = '')) %>% 
  mutate(subid = 'VP011',
         session = '3')

sub.vp011.ses.04.pant <- read_csv(file = paste(path,'VP011_04/ANT-VP011_04.csv', sep = '')) %>% 
  mutate(subid = 'VP011',
         session = '4')

sub.vp011 <- bind_rows(sub.vp011.ses.01.pant,sub.vp011.ses.03.pant, sub.vp011.ses.04.pant) 

## VP012

sub.vp012.ses.01.pant <- read_csv(file = paste(path,'VP012_01/ANT-VP012_01.csv', sep = '')) %>% 
  mutate(subid = 'VP012',
         session = '1')

sub.vp012.ses.03.pant <- read_csv(file = paste(path,'VP012_02/ANT-VP012_02.csv', sep = '')) %>% 
  mutate(subid = 'VP012',
         session = '3')
sub.vp012.ses.04.pant <- read_csv(file = paste(path,'VP012_04/ANT-VP012_04.csv', sep = '')) %>% 
  mutate(subid = 'VP012',
         session = '4')

sub.vp012 <- bind_rows(sub.vp012.ses.01.pant,sub.vp012.ses.03.pant,sub.vp012.ses.04.pant) 

## VP013

sub.vp013.ses.01.pant <- read_csv(file = paste(path,'VP013_01/ANT-VP013_01.csv', sep = '')) %>% 
  mutate(subid = 'VP013',
         session = '1')

sub.vp013.ses.03.pant <- read_csv(file = paste(path,'VP013_02/ANT-VP013_03.csv', sep = '')) %>% 
  mutate(subid = 'VP013',
         session = '3')

sub.vp013.ses.04.pant <- read_csv(file = paste(path,'VP013_04/ANT-VP013_04.csv', sep = '')) %>% 
  mutate(subid = 'VP013',
         session = '4')

sub.vp013 <- bind_rows(sub.vp013.ses.01.pant,sub.vp013.ses.03.pant,sub.vp013.ses.04.pant) 


## VP019

sub.vp019.ses.01.pant <- read_csv(file = paste(path,'VP019_01/ANT-VP019_01.csv', sep = '')) %>% 
  mutate(subid = 'VP019',
         session = '1')

sub.vp019.ses.03.pant <- read_csv(file = paste(path,'VP019_02/ANT-VP019_02.csv', sep = '')) %>% 
  mutate(subid = 'VP019',
         session = '3')
sub.vp019.ses.04.pant <- read_csv(file = paste(path,'VP019_04/ANT-VP019_04.csv', sep = '')) %>% 
  mutate(subid = 'VP019',
         session = '4')

sub.vp019 <- bind_rows(sub.vp019.ses.01.pant,sub.vp019.ses.03.pant,sub.vp019.ses.04.pant) 

## CP001

sub.cp001.ses.01.pant <- read_csv(file = paste(path,'CP001_01/ANT-CP001_01.csv', sep = '')) %>% 
  mutate(subid = 'CP001',
         session = '1')

sub.cp001.ses.03.pant <- read_csv(file = paste(path,'CP001_03/ANT-CP001_03.csv', sep = '')) %>% 
  mutate(subid = 'CP001',
         session = '3')


sub.cp001 <- bind_rows(sub.cp001.ses.01.pant,sub.cp001.ses.03.pant) 


## CP002

sub.cp002.ses.01.pant <- read_csv(file = paste(path,'CP002_01/ANT-CP002_01.csv', sep = '')) %>% 
  mutate(subid = 'CP002',
         session = '1')

sub.cp002.ses.03.pant <- read_csv(file = paste(path,'CP002/ANT-CP002.csv', sep = '')) %>% 
  mutate(subid = 'CP002',
         session = '3')


sub.cp002 <- bind_rows(sub.cp002.ses.01.pant,sub.cp002.ses.03.pant) 

## CP003

sub.cp003.ses.01.pant <- read_csv(file = paste(path,'CP003_01/ANT-CP003_01.csv', sep = '')) %>% 
  mutate(subid = 'CP003',
         session = '1')

sub.cp003.ses.03.pant <- read_csv(file = paste(path,'CP003_03/ANT-CP003_03.csv', sep = '')) %>% 
  mutate(subid = 'CP003',
         session = '3')


sub.cp003 <- bind_rows(sub.cp003.ses.01.pant,sub.cp003.ses.03.pant) 

## CP004

sub.cp004.ses.01.pant <- read_csv(file = paste(path,'CP004_01/ANT-CP004_01.csv', sep = '')) %>% 
  mutate(subid = 'CP004',
         session = '1')

sub.cp004.ses.03.pant <- read_csv(file = paste(path,'CP004_03/ANT-CP004_03.csv', sep = '')) %>% 
  mutate(subid = 'CP004',
         session = '3')


sub.cp004 <- bind_rows(sub.cp004.ses.01.pant,sub.cp004.ses.03.pant) 


## CP006

sub.cp006.ses.01.pant <- read_csv(file = paste(path,'CP006/ANT-CP006.csv', sep = '')) %>% 
  mutate(subid = 'CP006',
         session = '1')

sub.cp006.ses.03.pant <- read_csv(file = paste(path,'CP006_03/ANT-CP006_03.csv', sep = '')) %>% 
  mutate(subid = 'CP006',
         session = '3')


sub.cp006 <- bind_rows(sub.cp006.ses.01.pant,sub.cp006.ses.03.pant) 

## CP007

sub.cp007.ses.01.pant <- read_csv(file = paste(path,'CP007/ANT-CP007.csv', sep = '')) %>% 
  mutate(subid = 'CP007',
         session = '1')

sub.cp007.ses.03.pant <- read_csv(file = paste(path,'CP007_03/ANT-CP007_03.csv', sep = '')) %>% 
  mutate(subid = 'CP007',
         session = '3')


sub.cp007 <- bind_rows(sub.cp007.ses.01.pant,sub.cp007.ses.03.pant) 

## CP008

sub.cp008.ses.01.pant <- read_csv(file = paste(path,'CP008_01/ANT-CP008_01.csv', sep = '')) %>% 
  mutate(subid = 'CP008',
         session = '1')

sub.cp008.ses.03.pant <- read_csv(file = paste(path,'CP008_03/ANT-CP008_03.csv', sep = '')) %>% 
  mutate(subid = 'CP008',
         session = '3')


sub.cp008 <- bind_rows(sub.cp008.ses.01.pant,sub.cp008.ses.03.pant) 

## CP009

sub.cp009.ses.01.pant <- read_csv(file = paste(path,'CP009_01/ANT-CP009_01.csv', sep = '')) %>% 
  mutate(subid = 'CP009',
         session = '1')

sub.cp009.ses.03.pant <- read_csv(file = paste(path,'CP009_03/ANT-CP009_03.csv', sep = '')) %>% 
  mutate(subid = 'CP009',
         session = '3')


sub.cp009 <- bind_rows(sub.cp009.ses.01.pant,sub.cp009.ses.03.pant) 

## CP010

sub.cp010.ses.01.pant <- read_csv(file = paste(path,'CP010_01/ANT-CP010_01.csv', sep = '')) %>% 
  mutate(subid = 'CP010',
         session = '1')

sub.cp010.ses.03.pant <- read_csv(file = paste(path,'CP010_03/ANT-CP010_03.csv', sep = '')) %>% 
  mutate(subid = 'CP010',
         session = '3')


sub.cp010 <- bind_rows(sub.cp010.ses.01.pant,sub.cp010.ses.03.pant) 


## CP011

sub.cp011.ses.01.pant <- read_csv(file = paste(path,'CP011_01/ANT-CP011_01.csv', sep = '')) %>% 
  mutate(subid = 'CP011',
         session = '1')

sub.cp011.ses.03.pant <- read_csv(file = paste(path,'CP011_03/ANT-CP011_03.csv', sep = '')) %>% 
  mutate(subid = 'CP011',
         session = '3')


sub.cp011 <- bind_rows(sub.cp011.ses.01.pant,sub.cp011.ses.03.pant) 

## Combine all data up to VP012

data.to.vp012 <- bind_rows(sub.vp006,
                           sub.vp007,sub.vp008,sub.vp009,
                           sub.vp010,sub.vp011,sub.vp012,sub.vp013,sub.vp019, sub.cp001, sub.cp002, sub.cp003, sub.cp004, sub.cp006, sub.cp007, sub.cp008, sub.cp009, sub.cp010, sub.cp011) 

## Load data from VP013
manually_loaded <- c("VP006",
                    "VP007","VP008","VP009","VP010","VP011","VP012","VP013","VP019","CP001", "CP002", "CP003", "CP004", "CP006", "CP007", "CP008", "CP009", "CP010", "CP011")

path = "C:/Users/Jeane/Documents/PhD/Behavior_Analysis/PANT/"
all.subject.folders <- list.files(path)
subject.folders.from.vp013 <- all.subject.folders[!(all.subject.folders %in% manually_loaded)]

data.from.vp013 <- map_df(list.files(path = paste(path,subject.folders.from.vp013,sep = ''), full.names = T, 
                                     pattern = 'ANT-.*VP[0-9]*.*.csv', recursive = TRUE), read_csv) %>% 
  separate(subnum, into = c('subid','session'),  remove = FALSE) %>%
  mutate(session = str_remove(session,'0'))

data_df <- read.delim(file = paste(bids_folder,'participants.tsv', sep = ''), header = T, 
                      sep = '\t')

data_df$subid <- data_df$participant_id

all.data <- bind_rows(data.to.vp012, data.from.vp013)

all.data <- left_join(all.data, data_df, by = 'subid') %>% 
  mutate(group = case_when(group == 'lV1' ~ 'V1',
                           group == 'rV1' ~ 'V1',
                           group == 'rAIC' ~ 'rAIC',
                           group == 'noFeedback' ~ 'mental-rehearsal'))


```

Descriptive statistic for groups and histogramm Reaction Times (rt)

```{r}
by(data_df, data_df$group, summary)
table(data_df$group, data_df$sex)
hist(all.data$rt)

```


Eliminating extreme values 200 > RT > 1700ms (Ishigami & Klein, 2011)


```{r, echo = TRUE, message = FALSE}

all.data2 <- all.data %>% 
  filter(corr == 1)

Q1 <- quantile(all.data2$rt, probs=.25)
Q3 <- quantile(all.data2$rt, probs=.75)

Q1 <- quantile(all.data2$rt,0.025)
Q3 <- quantile(all.data2$rt,0.975)
iqr = Q3-Q1
upper_limit = 1700
lower_limit = 200

all.data2 <- all.data2 %>%
  subset(rt >= Q1& rt <= Q3)

diff <- dim(all.data)[1]-dim(all.data2)[1]
per <- diff/dim(all.data)[1]
print(paste(per, "% of the data has been removed"))
hist(all.data2$rt)

```





# 2. Explore data


```{r pressure, echo=TRUE, message =FALSE }

data.explore <- all.data2 %>% 
  filter(practice != 1) %>% 
  select(-subnum) %>% 
  mutate(cue_type = as_factor(case_when(cue == 1 ~ 'no cue',
                                        cue == 2 ~ 'center cue',
                                        cue == 3 ~ 'double cue',
                                        cue == 4 ~ 'spatial cue')),
         congruence_type = as_factor(case_when(flankercoherence == -1 ~ 'Incongruent',
                                               flankercoherence == 0  ~ 'Neutral',
                                               flankercoherence == 1 ~ 'Congruent')),
         corr_factor = as_factor(corr))

summ_data_all <- data.explore %>%
  group_by(subid,cue_type,congruence_type,session,group) %>% 
  summarise(meanRT = mean(rt),
            meanAcc = mean(corr))

summ_data_cue <- data.explore %>% 
  group_by(subid,  cue_type, session,group) %>% 
  summarise(meanRT = mean(rt),
            meanAcc = mean(corr))

summ_data_cue_corr <- data.explore %>% 
  filter(corr == 1) %>% 
  group_by(subid,  cue_type, session,group) %>% 
  summarise(meanRT = mean(rt))

summ_data_congruency <- data.explore %>% 
  group_by(subid,  congruence_type, session,group) %>% 
  summarise(meanRT = mean(rt),
            meanAcc = mean(corr))

summ_data_congruency_corr <- data.explore %>% 
  filter(corr == 1) %>% 
  group_by(subid,  congruence_type, session,group) %>% 
  summarise(meanRT = mean(rt))
```

# 3. Plot

Alerting Effect for correct response (No cue - double cue)

```{r, message= FALSE, warning=FALSE}
alert_data_corr <- data.explore %>% 
  filter(corr == 1,
         cue_type %in% c('double cue', 'no cue')) %>% 
  group_by(cue_type, session, subid, group) %>% 
  summarise(meanRT = mean(rt)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = cue_type, values_from = meanRT) %>% 
  mutate(alerting_effect = `no cue` - `double cue`)

alert_data_corr <- alert_data_corr%>%
   filter(!(subid %in% c('VP012', 'VP019', 'VP016')))

alert_data_corr %>% 
  group_by(session,group) %>% 
  summarise(meanAlertingEffect = mean(alerting_effect)) %>% 
  ungroup() %>% 
  ggplot() + 
  aes(x = session, y = meanAlertingEffect, group = group, color = group, fill = group) +
  geom_point(size = 3) + 
  geom_line(size = 1) + 
  geom_point(data = alert_data_corr,
             aes(x = session, y = alerting_effect, group = interaction(group, subid),
                 color = group), 
                 alpha = 0.3) +
  geom_line(data = alert_data_corr,
             aes(x = session, y = alerting_effect, group = interaction(group, subid),
                 color = group), 
                 alpha = 0.3) + 
  theme_rtfmri() +
  ylim(c(-20,160)) + 
  ylab('RT No Cue - RT Double Cue') +
  ggtitle(label = '', subtitle = 'only correct responses') -> alerting_plot_corr

alerting_plot_corr


```

Plot without individual lines and errorbars
```{r, message=FALSE}
label_session <- c("Pre rt-fMRI NFB", "Acute post", "3-months FU")
alert_data_corr<- alert_data_corr%>%
  mutate(group = case_when(group == 'V1' ~ 'V1',
                             group == 'rAIC' ~ 'rAIC',
                             group == 'mental-rehearsal' ~ 'mental-rehearsal'))

alert_data_corr %>% 
  group_by(session,group) %>% 
  summarise(meanAlertingEffect = mean(alerting_effect), se = sd(alerting_effect)/sqrt(length(alerting_effect))) %>% 
  ungroup() %>% 
  ggplot() + 
  aes(x = session, y = meanAlertingEffect, group = group, color = group, fill = group) +
  geom_point(size = 4) + 
  geom_line(size = 2) + 
  geom_errorbar(aes(ymin=meanAlertingEffect-se, ymax=meanAlertingEffect+se), width=.2)+
  theme_rtfmri() +
  ylab('RT No Cue - RT Double Cue') +
  scale_x_discrete(labels=label_session)+
  theme(legend.position = c(0.87, 0.25))+
  ylim(c(0,100)) + 
  ggtitle(label = 'Alerting Effect') -> alerting_plot_corr

alert_data_corr %>% 
    group_by(session,group) %>% 
    summarise(meanAlertingEffect = mean(alerting_effect), se = sd(alerting_effect)/sqrt(length(alerting_effect))) %>% 
    ungroup() %>% 
    ggplot() + 
    aes(x = session, y = meanAlertingEffect, group = group, color = group, fill = group) +
    geom_point(size = 2) + 
    geom_line(size = 1) + 
    geom_errorbar(aes(ymin=meanAlertingEffect-se, ymax=meanAlertingEffect+se), width=.2)+
    theme_rtfmri2() +
    ylab('Alerting effect (ms)') +
    scale_x_discrete(labels=label_session)+
    theme(legend.position = c(0.87, 0.25))+
    ylim(c(0,80))


```
 
Alerting effect all response (correct and not correct)

```{r, message = FALSE, warning=FALSE}
### all trials

alert_data <- data.explore %>% 
  filter(cue_type %in% c('double cue', 'no cue')) %>% 
  group_by(cue_type, session, subid, group) %>% 
  summarise(meanRT = mean(rt)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = cue_type, values_from = meanRT) %>% 
  mutate(alerting_effect = `no cue` - `double cue`)

#### Plot

alert_data %>% 
  group_by(session,group) %>% 
  summarise(meanAlertingEffect = mean(alerting_effect)) %>% 
  ungroup() %>% 
  ggplot() + 
  aes(x = session, y = meanAlertingEffect, group = group, color = group, fill = group) +
  geom_point(size = 4) + 
  geom_line(size = 2) + 
  geom_point(data = alert_data,
             aes(x = session, y = alerting_effect, group = interaction(group, subid),
                 color = group), 
             alpha = 0.3) +
  geom_line(data = alert_data,
            aes(x = session, y = alerting_effect, group = interaction(group, subid),
                color = group), 
            alpha = 0.3) + 
  theme_rtfmri() +
  ylab('RT No Cue - RT Double Cue') +
  ylim(c(-20,160)) + 
  ggtitle(label = 'Alerting Effect', subtitle = 'all responses') -> alerting_plot_All

alerting_plot_All
```

Without individual lines

```{r, message = FALSE, warning=FALSE}
alert_data %>% 
  group_by(session,group) %>% 
  summarise(meanAlertingEffect = mean(alerting_effect), se = sd(alerting_effect)/sqrt(length(alerting_effect))) %>% 
  ungroup() %>% 
  ggplot() + 
  aes(x = session, y = meanAlertingEffect, group = group, color = group, fill = group) +
  geom_point(size = 4) + 
  geom_line(size = 2) + 
  geom_errorbar(aes(ymin=meanAlertingEffect-se, ymax=meanAlertingEffect+se), width=.2)+
  theme_rtfmri() +
  ylab('RT No Cue - RT Double Cue') +
  ylim(c(0,100))+
  ggtitle(element_text('Alerting Effect', size = 20, hjust = 0.5))-> alerting_plot_All_Error

alerting_plot_All_Error
```

# 4. Stats Mixed ANOVA (within subject factor = session, between subject factor = group)

```{r}

library(ggpubr)

library(rstatix)

alert_data_corr %>%
  group_by(session, group) %>%
  get_summary_stats(alerting_effect, type = "mean_sd")

bxp <-ggboxplot(alert_data_corr, x= "group", y="alerting_effect",
                color = "session", palette = "jco")
bxp

```


# 4.1 Check assumptions

## 4.1.1 Outliers

```{r, warning=FALSE}

alert_data_corr %>%
  group_by(session,group) %>%
  identify_outliers(alerting_effect)

```

There are no extreme outlier

## 4.1.2 Normality assumption

```{r, warning=FALSE}
alert_data_corr %>%
  group_by(session,group) %>%
  shapiro_test(alerting_effect)

ggqqplot(alert_data_corr, "alerting_effect", ggtheme = theme_bw())+
  facet_grid(session~group)

```

rAIC Session 01 is slightly not normal distributed

## 4.1.3 Homogeneity of variance

```{r, warning=FALSE}
alert_data_corr %>%
  group_by(session) %>%
  levene_test(alerting_effect ~ group)


alert_data_corr_long <- alert_data_corr[,-c(6)]%>%
  group_by(subid)%>%
  pivot_wider(names_from = session, values_from = c('double cue', 'no cue'))

alert_data_corr_long <- alert_data_corr_long%>%
  mutate(alerting_effect_1 = `no cue_1`- `double cue_1`)

alert_data_corr_long <- alert_data_corr_long%>%
  mutate(alerting_effect_3 = `no cue_3`- `double cue_3`)

alert_data_corr_long <- alert_data_corr_long%>%
  mutate(alerting_effect_4 = `no cue_4`- `double cue_4`)

Alert2 <- alert_data_corr_long[-c(11,12,13,14),]
Alertfinal <- Alert2[-c(24,57),]
```

There is homogeneity of variances, as assessed by Levene's test (p > 0.05)
```{r, warning=FALSE}
box_m(alert_data_corr[, "alerting_effect", drop = FALSE], alert_data_corr$group)

```

There was homogeneity of covariances, as assessed by Box’s test of equality of covariance matrices (p > 0.001).


# 4.2 Mixed ANOVA
```{r, warning=FALSE}

res.aov <- anova_test(
  data = alert_data_corr, dv = alerting_effect, wid = subid,
  between = group, within = session
)
get_anova_table(res.aov)
```

There is a significant effect of time and a interaction between group and session on the alerting_effect. The main effect of group is not significant.

# 4.3 Post-hoc test

Effect of time at each level of group 
```{r, warnings = FALSE}
pwc2 <- alert_data_corr %>%
  group_by(group) %>%
  pairwise_t_test(
    alerting_effect ~ session, paired = TRUE, 
    p.adjust.method = "bonferroni"
  ) %>%
  select(-df, -statistic, -p) # Remove details
pwc2
```

Using pairwise paired t-test comparisons, it can be seen that for rAIC the mean anxiety score was significantly different between session 01 and session 03 and session 01 and session 04
