---
title: "ANT_analysis_CueType"
author: "Jeanette Popovova"
date: "1/24/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
### Libraries
library(tidyverse) # for data wrangling and plotting
library(ggpubr)
library(rstatix)
```

#Alerting Effect Analysis


## 1. Loading and prepare ANT data


```{r cars}
Alert <- read.csv("C:/Users/Jeane/Documents/PhD/Analysis_Paper1/NFB/Beh/final_Values_used/Alert_long.csv")

```

## Get summary 



```{r pressure, echo=FALSE}
Alert2_wide %>%
   group_by(group, type, session) %>%
   get_summary_stats(value, type = "mean_sd")
```

## 2. Test for Assumptions
```{r}
##Outliers

Alert2_wide %>%
  group_by(group, type, session) %>%
  identify_outliers(value)


## Normality

 
ggqqplot(Alert2_wide, "value", ggtheme = theme_bw()) +
  facet_grid(group + type ~ session, labeller = "label_both")

##Homogenity

Alert2_wide %>%
  group_by(group, session) %>%
  levene_test(value ~ type)

```


## 3. Get Boxplot

```{r}
Alert2_wide<-Alert2_wide%>%
  ungroup()

bxp <- ggplot(Alert2_wide, aes(x = group, y = value,
  colour = factor(session)))+
   geom_boxplot()+ facet_grid(cols = vars(type))


bxp

# Alert2_wide<- Alert2_wide%>%
#   subset(group!= 'noFeedback')
```


## 4. Mixed Model ANOVA Three-way (within-subject: session, type / between-subject: group)

```{r}
Alert2_wide$type<- as.factor(Alert2_wide$type)
Alert2_wide$session <- as.factor(Alert2_wide$session)
Alert2_wide$group <- as.factor(Alert2_wide$group)
Alert2_wide$subid <- as.factor(Alert2_wide$subid)

Alert2_wide <-Alert2_wide%>%
  ungroup()

 res.aov <- anova_test(
   data = Alert2_wide, dv = value, wid = subid,
   between = group, within = c(type, session)
 )

get_anova_table(res.aov)
 
 ##There is a three way interaction, now we compute simple two-way interaction between type and session for each group
```

There is a three way interaction between group, session and CueType, now we compute simple two-way interaction between type and session for each group



```{r}
 two.way <- Alert2_wide %>%
   group_by(group) %>%
   anova_test(dv = value, wid = subid, within = c(type, session))
 two.way
 
 # Extract anova table
 get_anova_table(two.way)
 
```
 
There was a statistically significant simple two-way interaction between type and session for the rAIC group but not V1

Now we can compute simple main effect of type at every level of session for th rAIC 
 
 
```{r}
 
 ##Now we can compute simple main effect of type at every level of session for th rAIC 
 time.effect <- Alert2_wide %>%
   group_by(group, type) %>%
   anova_test(dv = value, wid = subid, within = session) %>%
   get_anova_table()
 time.effect %>% filter(group == "rAIC")
 
#The simple main effect of session was significant for type:double cue
 
 pwc <- Alert2_wide %>%
   group_by(group, type) %>%
   pairwise_t_test(
     value ~ session, paired = TRUE, 
     p.adjust.method = "bonferroni"
   )
 pwc %>% filter(group == "rAIC") %>%
   select(-p)    # Remove p column
```


## 5. Boxplot with Effects

```{r}
 pwc <- pwc %>% add_xy_position(x = "group")
 pwc.filtered <- pwc %>% filter(group == "rAIC")
 bxp + 
   stat_pvalue_manual(pwc.filtered, tip.length = 0, hide.ns = TRUE) +
   labs(
     subtitle = get_test_label(res.aov, detailed = TRUE),
     caption = get_pwc_label(pwc)
   )
 
```

