---
title: "Corsi_Analysis"
output:
  html_document:
    df_print: paged
---

# 1. Load the data

```{r, warning=FALSE, echo=FALSE, include=FALSE}
### Libraries
library(tidyverse) # for data wrangling and plotting
# library(here)
# library(viridis)
# library(patchwork)

###Because some of the first data were saved with wrong naming scheme this ones are outside the folder and after loading them change the path

path = 'C:/Users/Jeane/Documents/PhD/Behavior_Analysis/corsiwrongName/'

bids_folder =  'C:/Users/Jeane/Documents/PhD/Behavior_Analysis/'



### ggplot theme

theme_rtfmri <- function(base_size = 11,
                         base_family = "",
                         base_line_size = base_size / 170,
                         base_rect_size = base_size / 170){
  theme_bw(base_size = base_size, 
           base_family = base_family,
           base_line_size = base_line_size) %+replace% 
    theme(
      plot.title = element_text(
        color = rgb(25, 43, 65, maxColorValue = 255), 
        face = "bold",
        hjust = 0),
      axis.title = element_text(
        color = rgb(105, 105, 105, maxColorValue = 255),
        size = rel(0.75)),
      axis.text = element_text(
        color = rgb(105, 105, 105, maxColorValue = 255),
        size = rel(0.5)),
      panel.grid.major = element_line(
        rgb(105, 105, 105, maxColorValue = 255),
        linetype = "dotted"),   
      panel.grid.minor = element_line(
        rgb(105, 105, 105, maxColorValue = 255),
        linetype = "dotted", 
        size = rel(4)), 
      
      complete = TRUE
    )
}

## VP006

sub.vp006.ses.01.corsi <- read_csv(file = paste(path,'jVP006_1/corsi-trial-jVP006_1.csv', sep = '')) %>% 
  mutate(subid = 'VP006',
         session = '1')

sub.vp006.ses.03.corsi <- read_csv(file = paste(path,'VP006_03/corsi-trial-VP006_03.csv', sep = '')) %>% 
  mutate(subid = 'VP006',
         session = '3')

sub.vp006.ses.04.corsi <- read_csv(file = paste(path,'VP006_04/corsi-trial-VP006_04.csv', sep = '')) %>% 
  mutate(subid = 'VP006',
         session = '4')


sub.vp006.corsi <- bind_rows(sub.vp006.ses.01.corsi,sub.vp006.ses.03.corsi, sub.vp006.ses.04.corsi) 


## VP007

sub.vp007.ses.01.corsi <- read_csv(file = paste(path,'VP007_01/corsi-trial-VP007_01.csv', sep = '')) %>% 
  mutate(subid = 'VP007',
         session = '1')

sub.vp007.ses.03.corsi <- read_csv(file = paste(path,'VP007_02/corsi-trial-VP007_02.csv', sep = '')) %>% 
  mutate(subid = 'VP007',
         session = '3')

sub.vp007.ses.04.corsi <- read_csv(file = paste(path,'VP007_04/corsi-trial-VP007_04.csv', sep = '')) %>% 
  mutate(subid = 'VP007',
         session = '4')


sub.vp007.corsi <- bind_rows(sub.vp007.ses.01.corsi,sub.vp007.ses.03.corsi, sub.vp007.ses.04.corsi) 

## VP008

sub.vp008.ses.01.corsi <- read_csv(file = paste(path,'VP008_01/corsi-trial-VP008_01.csv', sep = '')) %>% 
  mutate(subid = 'VP008',
         session = '1')

sub.vp008.ses.03.corsi <- read_csv(file = paste(path,'VP008_02/corsi-trial-VP008_02.csv', sep = '')) %>% 
  mutate(subid = 'VP008',
         session = '3')

sub.vp008.ses.04.corsi <- read_csv(file = paste(path,'VP008_04/corsi-trial-VP008_04.csv', sep = '')) %>% 
  mutate(subid = 'VP008',
         session = '4')

sub.vp008.corsi <- bind_rows(sub.vp008.ses.01.corsi,sub.vp008.ses.03.corsi, sub.vp008.ses.04.corsi) 

## VP009

sub.vp009.ses.01.corsi <- read_csv(file = paste(path,'VP009_01/corsi-trial-VP009_01.csv', sep = '')) %>% 
  mutate(subid = 'VP009',
         session = '1')

sub.vp009.ses.03.corsi <- read_csv(file = paste(path,'VP009_02/corsi-trial-VP009_02.csv', sep = '')) %>% 
  mutate(subid = 'VP009',
         session = '3')

sub.vp009.ses.04.corsi <- read_csv(file = paste(path,'VP009_04/corsi-trial-VP009_04.csv', sep = '')) %>% 
  mutate(subid = 'VP009',
         session = '4')

sub.vp009.corsi <- bind_rows(sub.vp009.ses.01.corsi,sub.vp009.ses.03.corsi, sub.vp009.ses.04.corsi) 


## VP010

sub.vp010.ses.01.corsi <- read_csv(file = paste(path,'VP010_01/corsi-trial-VP010_01.csv', sep = '')) %>% 
  mutate(subid = 'VP010',
         session = '1')

sub.vp010.ses.03.corsi <- read_csv(file = paste(path,'VP010_2/corsi-trial-VP010_2.csv', sep = '')) %>% 
  mutate(subid = 'VP010',
         session = '3')

sub.vp010.ses.04.corsi <- read_csv(file = paste(path,'VP010_04/corsi-trial-VP010_04.csv', sep = '')) %>% 
  mutate(subid = 'VP010',
         session = '4')

sub.vp010.corsi <- bind_rows(sub.vp010.ses.01.corsi,sub.vp010.ses.03.corsi, sub.vp010.ses.04.corsi) 

## VP011

sub.vp011.ses.01.corsi <- read_csv(file = paste(path,'VP011/corsi-trial-VP011.csv', sep = '')) %>% 
  mutate(subid = 'VP011',
         session = '1')

sub.vp011.ses.03.corsi <- read_csv(file = paste(path,'VP011_02/corsi-trial-VP011_02.csv', sep = '')) %>% 
  mutate(subid = 'VP011',
         session = '3')

sub.vp011.ses.04.corsi <- read_csv(file = paste(path,'VP011_04/corsi-trial-VP011_04.csv', sep = '')) %>% 
  mutate(subid = 'VP011',
         session = '4')

sub.vp011.corsi <- bind_rows(sub.vp011.ses.01.corsi,sub.vp011.ses.03.corsi,sub.vp011.ses.04.corsi) 

## VP012

sub.vp012.ses.01.corsi <- read_csv(file = paste(path,'VP012_01/corsi-trial-VP012_01.csv', sep = '')) %>% 
  mutate(subid = 'VP012',
         session = '1')

sub.vp012.ses.03.corsi <- read_csv(file = paste(path,'VP012_02/corsi-trial-VP012_02.csv', sep = '')) %>% 
  mutate(subid = 'VP012',
         session = '3')

sub.vp012.ses.04.corsi <- read_csv(file = paste(path,'VP012_04/corsi-trial-VP012_04.csv', sep = '')) %>% 
  mutate(subid = 'VP012',
         session = '4')

sub.vp012.corsi <- bind_rows(sub.vp012.ses.01.corsi,sub.vp012.ses.03.corsi,sub.vp012.ses.04.corsi) 

## VP013

sub.vp013.ses.01.corsi <- read_csv(file = paste(path,'VP013_01/corsi-trial-VP013_01.csv', sep = '')) %>% 
  mutate(subid = 'VP013',
         session = '1')

sub.vp013.ses.03.corsi <- read_csv(file = paste(path,'VP013_02/corsi-trial-VP013_03.csv', sep = '')) %>% 
  mutate(subid = 'VP013',
         session = '3')

sub.vp013.ses.04.corsi <- read_csv(file = paste(path,'VP013_04/corsi-trial-VP013_04.csv', sep = '')) %>% 
  mutate(subid = 'VP013',
         session = '4')

sub.vp013.corsi <- bind_rows(sub.vp013.ses.01.corsi,sub.vp013.ses.03.corsi,sub.vp013.ses.04.corsi) 



## VP019

sub.vp019.ses.01.corsi <- read_csv(file = paste(path,'VP019_01/corsi-trial-VP019_01.csv', sep = '')) %>% 
  mutate(subid = 'VP019',
         session = '1')

sub.vp019.ses.03.corsi <- read_csv(file = paste(path,'VP019_02/corsi-trial-VP019_02.csv', sep = '')) %>% 
  mutate(subid = 'VP019',
         session = '3')

sub.vp019.ses.04.corsi <- read_csv(file = paste(path,'VP019_04/corsi-trial-VP019_04.csv', sep = '')) %>% 
  mutate(subid = 'VP019',
         session = '4')

sub.vp019.corsi <- bind_rows(sub.vp019.ses.01.corsi,sub.vp019.ses.03.corsi,sub.vp019.ses.04.corsi) 


## CP001

sub.cp001.ses.01.corsi <- read_csv(file = paste(path,'CP001_01/corsi-trial-CP001_01.csv', sep = '')) %>% 
  mutate(subid = 'CP001',
         session = '1')

sub.cp001.ses.03.corsi <- read_csv(file = paste(path,'CP001_03/corsi-trial-CP001_03.csv', sep = '')) %>% 
  mutate(subid = 'CP001',
         session = '3')

sub.cp001.corsi <- bind_rows(sub.cp001.ses.01.corsi,sub.cp001.ses.03.corsi) 



## CP002

sub.cp002.ses.01.corsi <- read_csv(file = paste(path,'CP002_01/corsi-trial-CP002_01.csv', sep = '')) %>% 
  mutate(subid = 'CP001',
         session = '1')

sub.cp002.ses.03.corsi <- read_csv(file = paste(path,'CP002/corsi-trial-CP002.csv', sep = '')) %>% 
  mutate(subid = 'CP002',
         session = '3')

sub.cp002.corsi <- bind_rows(sub.cp002.ses.01.corsi,sub.cp002.ses.03.corsi) 



## CP003

sub.cp003.ses.01.corsi <- read_csv(file = paste(path,'CP003_01/corsi-trial-CP003_01.csv', sep = '')) %>% 
  mutate(subid = 'CP003',
         session = '1')

sub.cp003.ses.03.corsi <- read_csv(file = paste(path,'CP003_03/corsi-trial-CP003_03.csv', sep = '')) %>% 
  mutate(subid = 'CP003',
         session = '3')

sub.cp003.corsi <- bind_rows(sub.cp003.ses.01.corsi,sub.cp003.ses.03.corsi) 


## CP004

sub.cp004.ses.01.corsi <- read_csv(file = paste(path,'CP004_01/corsi-trial-CP004_01.csv', sep = '')) %>% 
  mutate(subid = 'CP004',
         session = '1')

sub.cp004.ses.03.corsi <- read_csv(file = paste(path,'CP004_03/corsi-trial-CP004_03.csv', sep = '')) %>% 
  mutate(subid = 'CP004',
         session = '3')

sub.cp004.corsi <- bind_rows(sub.cp004.ses.01.corsi,sub.cp004.ses.03.corsi) 

## CP007

sub.cp007.ses.01.corsi <- read_csv(file = paste(path,'CP007/corsi-trial-CP007.csv', sep = '')) %>% 
  mutate(subid = 'CP007',
         session = '1')

sub.cp007.ses.03.corsi <- read_csv(file = paste(path,'CP007_03/corsi-trial-CP007_03.csv', sep = '')) %>% 
  mutate(subid = 'CP007',
         session = '3')

sub.cp007.corsi <- bind_rows(sub.cp007.ses.01.corsi,sub.cp007.ses.03.corsi) 


## CP008

sub.cp008.ses.01.corsi <- read_csv(file = paste(path,'CP008_01/corsi-trial-CP008_01.csv', sep = '')) %>% 
  mutate(subid = 'CP008',
         session = '1')

sub.cp008.ses.03.corsi <- read_csv(file = paste(path,'CP008_03/corsi-trial-CP008_03.csv', sep = '')) %>% 
  mutate(subid = 'CP008',
         session = '3')

sub.cp008.corsi <- bind_rows(sub.cp008.ses.01.corsi,sub.cp008.ses.03.corsi) 

## CP009

sub.cp009.ses.01.corsi <- read_csv(file = paste(path,'CP009_01/corsi-trial-CP009_01.csv', sep = '')) %>% 
  mutate(subid = 'CP009',
         session = '1')

sub.cp009.ses.03.corsi <- read_csv(file = paste(path,'CP009_03/corsi-trial-CP009_03.csv', sep = '')) %>% 
  mutate(subid = 'CP009',
         session = '3')

sub.cp009.corsi <- bind_rows(sub.cp009.ses.01.corsi,sub.cp009.ses.03.corsi) 

## CP010

sub.cp010.ses.01.corsi <- read_csv(file = paste(path,'CP010_01/corsi-trial-CP010_01.csv', sep = '')) %>% 
  mutate(subid = 'CP009',
         session = '1')

sub.cp010.ses.03.corsi <- read_csv(file = paste(path,'CP010_03/corsi-trial-CP010_03.csv', sep = '')) %>% 
  mutate(subid = 'CP010',
         session = '3')

sub.cp010.corsi <- bind_rows(sub.cp010.ses.01.corsi,sub.cp010.ses.03.corsi) 


## CP011

sub.cp011.ses.01.corsi <- read_csv(file = paste(path,'CP011_01/corsi-trial-CP011_01.csv', sep = '')) %>% 
  mutate(subid = 'CP011',
         session = '1')

sub.cp011.ses.03.corsi <- read_csv(file = paste(path,'CP011_03/corsi-trial-CP011_03.csv', sep = '')) %>% 
  mutate(subid = 'CP011',
         session = '3')

sub.cp011.corsi <- bind_rows(sub.cp011.ses.01.corsi,sub.cp011.ses.03.corsi) 


path = 'E:/corsi/'

## Combine all data up to VP012

data.to.vp012.corsi <- bind_rows(sub.vp006.corsi,
                           sub.vp007.corsi,sub.vp008.corsi,sub.vp009.corsi,
                           sub.vp010.corsi,sub.vp011.corsi,sub.vp012.corsi, sub.vp013.corsi, sub.vp019.corsi, sub.cp001.corsi, sub.cp002.corsi, sub.cp003.corsi, sub.cp004.corsi, sub.cp007.corsi,
                           sub.cp008.corsi, sub.cp009.corsi, sub.cp010.corsi, sub.cp011.corsi) 

## Load data from VP013
manually_loaded <- c("VP006",
                     "VP007","VP008","VP009","VP010","VP011","VP012", "VP013", "VP019", "CP001", "CP002", "CP003", "CP004", "CP007", "CP008", "CP009", "CP010", "CP011")



path = "C:/Users/Jeane/Documents/PhD/Behavior_Analysis/corsi/data/"


all.subject.folders <- list.files(path)
subject.folders.from.vp013.corsi <- all.subject.folders[!(all.subject.folders %in% manually_loaded)]

data.from.vp013.corsi <- map_df(list.files(path = paste(path,subject.folders.from.vp013.corsi,sep = ''), full.names = T, 
                                     pattern = 'corsi-trial-.*VP[0-9]*.*.csv', recursive = TRUE), read_csv) %>% 
  separate(subnum, into = c('subid','session'),  remove = FALSE) %>%
  mutate(session = str_remove(session,'0'))

data_df <- read.delim(file = paste(bids_folder,'participants.tsv', sep = ''), header = T, 
                      sep = '\t')

data_df$subid <- data_df$participant_id

```

# 2. Get the max corsi spam for each session 

```{r, message=FALSE, warning=FALSE}
all.data.corsi <- bind_rows(data.to.vp012.corsi, data.from.vp013.corsi)
all.data.corsi <- inner_join(all.data.corsi, data_df, by = 'subid') %>% 
  filter(type != 'P', allcorr == 1) %>%   
  mutate(group = case_when(group == 'lV1' ~ 'V1',
                                                                                                                                         group == 'rV1' ~ 'V1',
                                                                                                                                         group == 'rAIC' ~ 'rAIC',
                           group == 'noFeedback' ~ 'noFeedback'))


## Get the maximum span for each participant

summarized_max_corsi <- all.data.corsi %>% 
  group_by(subid, session, group) %>% 
  summarise(maxCorsi = max(numcorr)) %>% 
  ungroup()
```

# 3. Plot the corsi spam for each group over session

```{r,  warning=FALSE}
summarized_max_corsi %>% 
  group_by(session,group) %>% 
  summarise(meanMaxCorsi = mean(maxCorsi)) %>% 
  ungroup() %>% 
  ggplot() + 
  aes(x = session, y = meanMaxCorsi, group = group, color = group) + 
  geom_point(size = 3) + 
  geom_line(size = 1) + 
  geom_point(data = summarized_max_corsi,
             aes(x = session, y = maxCorsi, group = interaction(group, subid),
                 color = group), 
             alpha = 0.3) +
  geom_line(data = summarized_max_corsi,
            aes(x = session, y = maxCorsi, group = interaction(group, subid),
                color = group), 
            alpha = 0.3) + 
  theme_rtfmri() + 
  ggtitle(label = 'Maximum Corsi Span') -> plot

plot
```

# 4. Stats

## 4.1 Check assumptions

### 4.1.1 Outliers

```{r, warning=FALSE}

library(ggpubr)

library(rstatix)
summarized_max_corsi%>%
  group_by(session,group) %>%
  identify_outliers(maxCorsi)

```

There are no extreme outlier

### 4.1.2 Normality assumption

```{r, warning=FALSE}
summarized_max_corsi %>%
  group_by(session,group) %>%
  shapiro_test(maxCorsi)

ggqqplot(summarized_max_corsi, "maxCorsi", ggtheme = theme_bw())+
  facet_grid(session~group)

```

rAIC Session 01 is slightly not normal distributed

### 4.1.3 Homogeneity of variance

```{r, warning=FALSE}
summarized_max_corsi %>%
  group_by(session) %>%
  levene_test(maxCorsi ~ group)
```

There is homogeneity of variances, as assessed by Levene's test (p > 0.05)

```{r, warning=FALSE}
box_m(summarized_max_corsi[, "maxCorsi", drop = FALSE], summarized_max_corsi$group)

```

There was homogeneity of covariances, as assessed by Box’s test of equality of covariance matrices (p > 0.001).


## 4.2 ANOVA
```{r}
res.aov <- anova_test(
  data = summarized_max_corsi, dv = maxCorsi, wid = subid,
  between = group, within = session
)
get_anova_table(res.aov)
```

No significant two-way interaction was found


## 4.3 Posthoc test

### 4.3.1 Test for groups

```{r}
summarized_max_corsi %>%
  pairwise_t_test(
    maxCorsi ~ group, 
    p.adjust.method = "bonferroni"
  )
```
There is a significant difference in max Corsi spam between the rAIC and V1 group (p<0.05)

### 4.3.2 Test for session

```{r}
summarized_max_corsi %>%
  pairwise_t_test(
    maxCorsi ~ session, 
    p.adjust.method = "bonferroni"
  )
```

There is no significant difference between sessions
