---
title: "Switcher"
author: "Jeanette Popovova"
date: "1/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Load data 

```{r, warning=FALSE, echo=FALSE, error=TRUE, include=FALSE}
### Libraries
library(tidyverse) # for data wrangling and plotting

source('rtfmri_theme.R')



path = 'C:/Users/Jeane/Documents/PhD/Behavior_Analysis/switcherwrongName/'

bids_folder = 'C:/Users/Jeane/Documents/PhD/Behavior_Analysis/'

### Messy naming conventions up to participant 12 

## Manual wrangling

## VP006

sub.vp006.ses.01.switcher <- read_csv(file = paste(path,'jVP006_1/switch-summary-jVP006_1.csv', sep = '')) %>% 
  mutate(subid = 'VP006',
         session = '1')

sub.vp006.ses.03.switcher <- read_csv(file = paste(path,'VP006_03/switch-summary-VP006_03.csv', sep = '')) %>% 
  mutate(subid = 'VP006',
         session = '3')

sub.vp006.ses.04.switcher <- read_csv(file = paste(path,'VP006_04/switch-summary-VP006_04.csv', sep = '')) %>% 
  mutate(subid = 'VP006',
         session = '4')


sub.vp006.switcher <- bind_rows(sub.vp006.ses.01.switcher,sub.vp006.ses.03.switcher, sub.vp006.ses.04.switcher) 

sub.vp006.switcher$matchlast <- as.numeric(sub.vp006.switcher$matchlast)
## VP007

sub.vp007.ses.01.switcher <- read_csv(file = paste(path,'VP007_01/switch-summary-VP007_01.csv', sep = '')) %>% 
  mutate(subid = 'VP007',
         session = '1')

sub.vp007.ses.03.switcher <- read_csv(file = paste(path,'VP007_02/switch-summary-VP007_02.csv', sep = '')) %>% 
  mutate(subid = 'VP007',
         session = '3')

sub.vp007.ses.04.switcher <- read_csv(file = paste(path,'VP007_04/switch-summary-VP007_04.csv', sep = '')) %>% 
  mutate(subid = 'VP007',
         session = '4')


sub.vp007.switcher <- bind_rows(sub.vp007.ses.01.switcher,sub.vp007.ses.03.switcher, sub.vp007.ses.04.switcher) 
sub.vp007.switcher$matchlast <- as.numeric(sub.vp007.switcher$matchlast)

## VP008

sub.vp008.ses.01.switcher <- read_csv(file = paste(path,'VP008_01/switch-summary-VP008_01.csv', sep = '')) %>% 
  mutate(subid = 'VP008',
         session = '1')

sub.vp008.ses.03.switcher <- read_csv(file = paste(path,'VP008_02/switch-summary-VP008_02.csv', sep = '')) %>% 
  mutate(subid = 'VP008',
         session = '3')

sub.vp008.ses.04.switcher <- read_csv(file = paste(path,'VP008_04/switch-summary-VP008_04.csv', sep = '')) %>% 
  mutate(subid = 'VP008',
         session = '4')

sub.vp008.switcher <- bind_rows(sub.vp008.ses.01.switcher,sub.vp008.ses.03.switcher, sub.vp008.ses.04.switcher) 
sub.vp008.switcher$matchlast <- as.numeric(sub.vp008.switcher$matchlast)
## VP009

sub.vp009.ses.01.switcher <- read_csv(file = paste(path,'VP009_01/switch-summary-VP009_01.csv', sep = '')) %>% 
  mutate(subid = 'VP009',
         session = '1') %>%
  mutate(matchlast = as.numeric(case_when(matchlast == '0NA' ~ '0',
                                          T ~ matchlast)))

sub.vp009.ses.03.switcher <- read_csv(file = paste(path,'VP009_02/switch-summary-VP009_02.csv', sep = '')) %>% 
  mutate(subid = 'VP009',
         session = '3')

sub.vp009.ses.04.switcher <- read_csv(file = paste(path,'VP009_04/switch-summary-VP009_04.csv', sep = '')) %>% 
  mutate(subid = 'VP009',
         session = '4')

sub.vp009.switcher <- bind_rows(sub.vp009.ses.01.switcher,sub.vp009.ses.03.switcher, sub.vp009.ses.04.switcher) 

sub.vp009.switcher$matchlast <- as.numeric(sub.vp009.switcher$matchlast)
## VP010

sub.vp010.ses.01.switcher <- read_csv(file = paste(path,'VP010_01/switch-summary-VP010_01.csv', sep = '')) %>% 
  mutate(subid = 'VP010',
         session = '1')

sub.vp010.ses.03.switcher <- read_csv(file = paste(path,'VP010_2/switch-summary-VP010_2.csv', sep = '')) %>% 
  mutate(subid = 'VP010',
         session = '3')

sub.vp010.ses.04.switcher <- read_csv(file = paste(path,'VP010_04/switch-summary-VP010_04.csv', sep = '')) %>% 
  mutate(subid = 'VP010',
         session = '4')

sub.vp010.switcher <- bind_rows(sub.vp010.ses.01.switcher,sub.vp010.ses.03.switcher, sub.vp010.ses.04.switcher) 

sub.vp010.switcher$matchlast <- as.numeric(sub.vp010.switcher$matchlast)

## VP011

sub.vp011.ses.01.switcher <- read_csv(file = paste(path,'VP011/switch-summary-VP011.csv', sep = '')) %>% 
  mutate(subid = 'VP011',
         session = '1')

sub.vp011.ses.03.switcher <- read_csv(file = paste(path,'VP011_02/switch-summary-VP011_02.csv', sep = '')) %>% 
  mutate(subid = 'VP011',
         session = '3')

sub.vp011.ses.04.switcher <- read_csv(file = paste(path,'VP011_04/switch-summary-VP011_04.csv', sep = '')) %>% 
  mutate(subid = 'VP011',
         session = '4')

sub.vp011.switcher <- bind_rows(sub.vp011.ses.01.switcher,sub.vp011.ses.03.switcher,sub.vp011.ses.04.switcher) 
sub.vp011.switcher$matchlast <- as.numeric(sub.vp011.switcher$matchlast)
## VP012

sub.vp012.ses.01.switcher <- read_csv(file = paste(path,'VP012_01/switch-summary-VP012_01.csv', sep = '')) %>% 
  mutate(subid = 'VP012',
         session = '1')

sub.vp012.ses.03.switcher <- read_csv(file = paste(path,'VP012_02/switch-summary-VP012_02.csv', sep = '')) %>% 
  mutate(subid = 'VP012',
         session = '3')

sub.vp012.ses.04.switcher <- read_csv(file = paste(path,'VP012_04/switch-summary-VP012_04.csv', sep = '')) %>% 
  mutate(subid = 'VP012',
         session = '4')

sub.vp012.switcher <- bind_rows(sub.vp012.ses.01.switcher,sub.vp012.ses.03.switcher,sub.vp012.ses.04.switcher) 
sub.vp012.switcher$matchlast <- as.numeric(sub.vp012.switcher$matchlast)
## VP013

sub.vp013.ses.01.switcher <- read_csv(file = paste(path,'VP013_01/switch-summary-VP013_01.csv', sep = '')) %>% 
  mutate(subid = 'VP013',
         session = '1') 

sub.vp013.ses.03.switcher <- read_csv(file = paste(path,'VP013_02/switch-summary-VP013_03.csv', sep = '')) %>% 
  mutate(subid = 'VP013',
         session = '3')%>%
  mutate(matchlast=as.numeric(matchlast))


sub.vp013.ses.04.switcher <- read_csv(file = paste(path,'VP013_04/switch-summary-VP013_04.csv', sep = '')) %>% 
  mutate(subid = 'VP013',
         session = '4')

sub.vp013.switcher <- bind_rows(sub.vp013.ses.01.switcher,sub.vp013.ses.03.switcher,sub.vp013.ses.04.switcher) 
sub.vp013.switcher$matchlast <- as.numeric(sub.vp013.switcher$matchlast)


## VP019

sub.vp019.ses.01.switcher <- read_csv(file = paste(path,'VP019_01/switch-summary-VP019_01.csv', sep = '')) %>% 
  mutate(subid = 'VP019',
         session = '1')

sub.vp019.ses.03.switcher <- read_csv(file = paste(path,'VP019_02/switch-summary-VP019_02.csv', sep = '')) %>% 
  mutate(subid = 'VP019',
         session = '3')

sub.vp019.ses.04.switcher <- read_csv(file = paste(path,'VP019_04/switch-summary-VP019_04.csv', sep = '')) %>% 
  mutate(subid = 'VP019',
         session = '4')

sub.vp019.switcher <- bind_rows(sub.vp019.ses.01.switcher,sub.vp019.ses.03.switcher,sub.vp019.ses.04.switcher) 

sub.vp019.switcher$matchlast <- as.numeric(sub.vp019.switcher$matchlast)


## CP001

sub.cp001.ses.01.switcher <- read_csv(file = paste(path,'CP001_01/switch-summary-CP001_01.csv', sep = '')) %>% 
  mutate(subid = 'CP001',
         session = '1')%>%
  mutate(matchlast = as.numeric(case_when(matchlast == '0NA' ~ '0',
                                          T ~ matchlast)))

sub.cp001.ses.03.switcher <- read_csv(file = paste(path,'CP001_03/switch-summary-CP001_03.csv', sep = '')) %>% 
  mutate(subid = 'CP001',
         session = '3')

sub.cp001.ses.01.switcher$matchlast<- as.numeric(sub.cp001.ses.01.switcher$matchlast)

sub.cp001.switcher <- bind_rows(sub.cp001.ses.01.switcher,sub.cp001.ses.03.switcher) 

sub.cp001.switcher$matchlast <- as.numeric(sub.cp001.switcher$matchlast)

## CP002

sub.cp002.ses.01.switcher <- read_csv(file = paste(path,'CP002_01/switch-summary-CP002_01.csv', sep = '')) %>% 
  mutate(subid = 'CP002',
         session = '1')

sub.cp002.ses.03.switcher <- read_csv(file = paste(path,'CP002/switch-summary-CP002.csv', sep = '')) %>% 
  mutate(subid = 'CP002',
         session = '3')



sub.cp002.switcher <- bind_rows(sub.cp002.ses.01.switcher,sub.cp002.ses.03.switcher) 

sub.cp002.switcher$matchlast <- as.numeric(sub.cp002.switcher$matchlast)


## CP003

sub.cp003.ses.01.switcher <- read_csv(file = paste(path,'CP003_01/switch-summary-CP003_01.csv', sep = '')) %>% 
  mutate(subid = 'CP003',
         session = '1')

sub.cp003.ses.03.switcher <- read_csv(file = paste(path,'CP003_03/switch-summary-CP003_03.csv', sep = '')) %>% 
  mutate(subid = 'CP003',
         session = '3')



sub.cp003.switcher <- bind_rows(sub.cp003.ses.01.switcher,sub.cp003.ses.03.switcher) 

sub.cp003.switcher$matchlast <- as.numeric(sub.cp003.switcher$matchlast)

## CP004

sub.cp004.ses.01.switcher <- read_csv(file = paste(path,'CP004_01/switch-summary-CP004_01.csv', sep = '')) %>% 
  mutate(subid = 'CP004',
         session = '1') %>%
  mutate(matchlast = as.numeric(case_when(matchlast == '0NA' ~ '0',
                                   T ~ matchlast)))

sub.cp004.ses.03.switcher <- read_csv(file = paste(path,'CP004_03/switch-summary-CP004_03.csv', sep = '')) %>% 
  mutate(subid = 'CP004',
         session = '3')



sub.cp004.switcher <- bind_rows(sub.cp004.ses.01.switcher,sub.cp004.ses.03.switcher) 

sub.cp004.switcher$matchlast <- as.numeric(sub.cp004.switcher$matchlast)

## CP006

sub.cp006.ses.01.switcher <- read_csv(file = paste(path,'CP006/switch-summary-CP006.csv', sep = '')) %>% 
  mutate(subid = 'CP006',
         session = '1') %>%
         mutate(matchlast = as.numeric(case_when(matchlast == '0NA' ~ '0',
                                                         T ~ matchlast)))

sub.cp006.ses.03.switcher <- read_csv(file = paste(path,'CP006_03/switch-summary-CP006_03.csv', sep = '')) %>% 
  mutate(subid = 'CP006',
         session = '3')



sub.cp006.switcher <- bind_rows(sub.cp006.ses.01.switcher,sub.cp006.ses.03.switcher) 

sub.cp006.switcher$matchlast <- as.numeric(sub.cp006.switcher$matchlast)

## CP007

sub.cp007.ses.01.switcher <- read_csv(file = paste(path,'CP007/switch-summary-CP007.csv', sep = '')) %>% 
  mutate(subid = 'CP007',
         session = '1')

sub.cp007.ses.03.switcher <- read_csv(file = paste(path,'CP007_03/switch-summary-CP007_03.csv', sep = '')) %>% 
  mutate(subid = 'CP007',
         session = '3')



sub.cp007.switcher <- bind_rows(sub.cp007.ses.01.switcher,sub.cp007.ses.03.switcher) 

sub.cp007.switcher$matchlast <- as.numeric(sub.cp007.switcher$matchlast)

## CP008

sub.cp008.ses.01.switcher <- read_csv(file = paste(path,'CP008_01/switch-summary-CP008_01.csv', sep = '')) %>% 
  mutate(subid = 'CP008',
         session = '1')

sub.cp008.ses.03.switcher <- read_csv(file = paste(path,'CP008_03/switch-summary-CP008_03.csv', sep = '')) %>% 
  mutate(subid = 'CP008',
         session = '3')



sub.cp008.switcher <- bind_rows(sub.cp008.ses.01.switcher,sub.cp008.ses.03.switcher) 

sub.cp008.switcher$matchlast <- as.numeric(sub.cp008.switcher$matchlast)

## CP009

sub.cp009.ses.01.switcher <- read_csv(file = paste(path,'CP009_01/switch-summary-CP009_01.csv', sep = '')) %>% 
  mutate(subid = 'CP009',
         session = '1')

sub.cp009.ses.03.switcher <- read_csv(file = paste(path,'CP009_03/switch-summary-CP009_03.csv', sep = '')) %>% 
  mutate(subid = 'CP009',
         session = '3') %>%
  mutate(matchlast = as.numeric(case_when(matchlast == '0NA' ~ '0',
                                          T ~ matchlast)))



sub.cp009.switcher <- bind_rows(sub.cp009.ses.01.switcher,sub.cp009.ses.03.switcher) 

sub.cp009.switcher$matchlast <- as.numeric(sub.cp009.switcher$matchlast)

## CP010

sub.cp010.ses.01.switcher <- read_csv(file = paste(path,'CP010_01/switch-summary-CP010_01.csv', sep = '')) %>% 
  mutate(subid = 'CP010',
         session = '1')

sub.cp010.ses.03.switcher <- read_csv(file = paste(path,'CP010_03/switch-summary-CP010_03.csv', sep = '')) %>% 
  mutate(subid = 'CP010',
         session = '3')



sub.cp010.switcher <- bind_rows(sub.cp010.ses.01.switcher,sub.cp010.ses.03.switcher) 

sub.cp010.switcher$matchlast <- as.numeric(sub.cp010.switcher$matchlast)

## CP011

sub.cp011.ses.01.switcher <- read_csv(file = paste(path,'CP011_01/switch-summary-CP011_01.csv', sep = '')) %>% 
  mutate(subid = 'CP011',
         session = '1') %>%
  mutate(matchlast = as.numeric(case_when(matchlast == '0NA' ~ '0',
                                   T ~ matchlast)))

sub.cp011.ses.03.switcher <- read_csv(file = paste(path,'CP011_03/switch-summary-CP011_03.csv', sep = '')) %>% 
  mutate(subid = 'CP011',
         session = '3')



sub.cp011.switcher <- bind_rows(sub.cp011.ses.01.switcher,sub.cp011.ses.03.switcher) 

sub.cp011.switcher$matchlast <- as.numeric(sub.cp011.switcher$matchlast)

## Combine all data up to VP013

data.to.vp012.switcher <- bind_rows(sub.vp006.switcher,                             sub.vp007.switcher,sub.vp008.switcher,sub.vp009.switcher,                        sub.vp010.switcher,sub.vp011.switcher,sub.vp012.switcher, sub.vp013.switcher, sub.vp019.switcher, sub.cp001.switcher, sub.cp002.switcher, sub.cp003.switcher, sub.cp004.switcher, sub.cp007.switcher,sub.cp008.switcher, sub.cp009.switcher, sub.cp010.switcher, sub.cp011.switcher) 

```

```{r, warning=FALSE, message=FALSE, include=FALSE}
## Load data from VP013
manually_loaded <- c("VP006",
                     "VP007","VP008","VP009","VP010","VP011","VP012", "VP013", "VP019", "CP001", "CP002", "CP003", "CP004", "CP007", "CP008", "CP009", "CP010", "CP011")




path = "C:/Users/Jeane/Documents/PhD/Behavior_Analysis/switcher/"

all.subject.folders <- list.files(path)
subject.folders.from.vp014.switcher <- all.subject.folders[!(all.subject.folders %in% manually_loaded)]



files.from.vp014.switcher <- list.files(path = paste(path,subject.folders.from.vp014.switcher,sep = ''), full.names = T, 
                                     pattern = 'switch-summary-.*VP[0-9]*.*.csv', recursive = TRUE)


data.from.vp014.switcher <- files.from.vp014.switcher %>% 
  map_df(~read_csv(.,col_types = cols(
    matchlast = col_character()
  ))) %>% 
  separate(subNum, into = c('subid','session'),  remove = FALSE) %>%
  mutate(session = str_remove(session,'0'),
         matchlast = as.numeric(case_when(matchlast == '0NA' ~ '0',
                                          T ~ matchlast)))


data_df <- read.delim(file = paste(bids_folder,'participants.tsv', sep = ''), header = T, 
                      sep = '\t')

data_df$subid <- data_df$participant_id

# Get all the switcher data

all.data.switcher <- bind_rows(data.to.vp012.switcher, data.from.vp014.switcher)

all.data.switcher <- inner_join(all.data.switcher, data_df, by = 'subid') %>% 
  mutate(group = case_when(group == 'lV1' ~ 'V1',
                           group == 'rV1' ~ 'V1',
                           group == 'rAIC' ~ 'rAIC',
                           group == 'noFeedback' ~ 'noFeedback'))

```

# 2. Compute Mean of Errors and response time

```{r, warning=FALSE, message=FALSE}
summarized_switcher <- all.data.switcher %>% 
  group_by(testtype, subid, session, group) %>% 
  summarise(numErr = mean(numerr),
            matchlast = mean(matchlast),
            tooslow = mean(tooslow),
            waittime = mean(waittime),
            perftime = mean(perftime),
            medtime = mean(medtime))

```

# 3. Plot Error and Response time

```{r, message=FALSE}
#perftime

summarized_switcher %>% 
  group_by(testtype, session, group) %>% 
  summarise(meanPerfTime = mean(perftime),
            meanNumErr = mean(numErr)) %>% 
  ungroup() %>% 
  ggplot() + 
  aes(x = session, y = meanPerfTime, group = group, color = group) + 
  geom_point(size = 3) + 
  geom_line(size = 1) + 
  geom_point(data = summarized_switcher,
             aes(x = session, y = perftime, group = interaction(group, subid),
                 color = group), 
             alpha = 0.3) +
  geom_line(data = summarized_switcher,
            aes(x = session, y = perftime, group = interaction(group, subid),
                color = group), 
            alpha = 0.3) + 
  theme_rtfmri() + 
  ggtitle(label = 'Mean Performance Time') + 
  facet_wrap(.~testtype)

#number of errors

summarized_switcher %>% 
  group_by(testtype, session, group) %>% 
  summarise(meanPerfTime = mean(perftime),
            meanNumErr = mean(numErr)) %>% 
  ungroup() %>% 
  ggplot() + 
  aes(x = session, y = meanNumErr, group = group, color = group) + 
  geom_point(size = 3) + 
  geom_line(size = 1) + 
  geom_point(data = summarized_switcher,
             aes(x = session, y = numErr, group = interaction(group, subid),
                 color = group), 
             alpha = 0.3) +
  geom_line(data = summarized_switcher,
            aes(x = session, y = numErr, group = interaction(group, subid),
                color = group), 
            alpha = 0.3) + 
  theme_rtfmri() + 
  ggtitle(label = 'Mean Number of Errors') + 
  facet_wrap(.~testtype)
```

# 4. Stats

## 4.1 Check assumptions

### 4.1.1 Outlier


```{r, warning=FALSE}

library(ggpubr)

library(rstatix)
summarized_switcher%>%
  group_by(session,group) %>%
  identify_outliers(numErr)

```

There are no extreme outlier

### 4.1.2 Normality assumption

```{r, warning=FALSE}
summarized_switcher %>%
  group_by(session,group) %>%
  shapiro_test(numErr)

ggqqplot(summarized_switcher, "numErr", ggtheme = theme_bw())+
  facet_grid(session~group)

```

rAIC Session 01 is slightly not normal distributed

### 4.1.3 Homogeneity of variance

```{r, warning=FALSE}
summarized_switcher %>%
  group_by(session) %>%
  levene_test(numErr ~ group)
```

There is homogeneity of variances, as assessed by Levene's test (p > 0.05)

```{r, warning=FALSE}
box_m(summarized_switcher[, "numErr", drop = FALSE], summarized_switcher$group)

```

There was homogeneity of covariances, as assessed by Box’s test of equality of covariance matrices (p > 0.001).

## 4.2 Stats - non-parametric two-way ANOVA (robust ANOVA)

```{r}
if(!require(WRS2)){install.packages("WRS2")}
if(!require(multcompView)){install.packages("multcompView")}
if(!require(psych)){install.packages("psych")}
library(WRS2)

pbad2way(numErr ~ group + session + group:session,
         data = summarized_switcher,
         est = "mom",    # modified M-estimator
         nboot = 5000)   # number of bootstrap samples
                         # a higher number will take longer to compute
```


